A tutorial of Bayesian beta regressions with brms in R

### 2025-02-06 manuscript/manuscript.qmd
edit manuscript

The main practical advantage of Bayesian regression models over maximum-likelihood-based frequentist regression models, like those fitted with the lme4 package [@bates2015], is that Bayesian regression models don't suffer from the convergence issues that models fitted in lme4 [@bates2015] and other packages [@cribarineto2010] that fit frequentist models do, independent of sample size. A second, long-term advantage is that Bayesian regression models allow researchers to statistically re-use information from previous studies by specifying informative priors. While prior specification is one of the main features of Bayesian inference, in this tutorial we will use the default priors as set by brms. These are sensible priors estimated from the data that facilitate convergence but bear virtually no influence on the estimated posteriors. Specifying priors requires a great deal of precise quantitative knowledge, which in most areas of phonetics we still do not possess, so that using default uninformative priors is, for the time being, theoretically sound.

@@

# Case study 1: voicing within consonant closure  {#sec-case-1}

For the first case study, we will model the proportion of voicing within consonant closure. The measurements come from a data set of audio and electroglottographic (EGG) recordings of 19 speakers of Northwestern Italian [@coretta2019k; @coretta2020b]. The participants read frame sentences which included target words of the form /CVCo/, where /C/ was either /k, t, p/ in all permutations and /V/ was either /i, e, a, ɔ, u/ (two resulting words, /peto/ and /kako/ were excluded because they are profanities), for a total of 43 target words. There were 4 different frame sentence: *Scrivete X sul foglio* 'Write X on the sheet', *Ha detto X sei volte* 'She said X six times', *Sentivo X di nuovo* 'I heard X again', *Ripete X da sempre* 'She's been repeating X since ever'. There is a total of 172 trials per participant (3,268 grand total). The actual observation count is 2,419, after removing speech errors, EGG measurement errors, and cases in which voicing ceased before the closure onset/after the closure offset of the second /C/.

The proportion of voicing during the closure of the second /C/ was calculated as the proportion of contiguous voicing duration after closure onset to total duration of closure. The following code chunk attaches the tidyverse packages [for reading and wrangling data, @wickham2019] and loads the `ita_egg` tibble (data frame). The tibble is filtered so as to remove voicing proportions (`voi_clo_prop`) that are smaller than 0 and greater than 1. The variables `vowel` and `c2` are converted to factors to specify the order of the levels.

@@

@tbl-ita-egg shows the first ten rows of the tibble (only relevant columns are included).

@@

@fig-ita-egg shows the raw voicing duration proportion values split by vowel /i, e, a, ɔ, u/ and second consonant /k, t, p/ in the /CVCo/ target words. The plot suggests that, on average, the voicing proportion is slightly lower with /k/ than with /t, p/. Moreover, there is greater variability between vowels in /t, p/ than in /k/. We will use a beta regression model to assess these patterns. \["expectations" XXX\]

@@

We will use brms to fit Bayesian beta regressions [@burkner2017]. The model has voicing proportion as the outcome variable and the following terms: an interaction between vowel (/i, e, a, ɔ, u/) and second consonant C2 (/k, t, p/), centred speech rate (number of syllables per second); as varying (aka random) terms, by-speaker varying coefficients for the vowel/consonant interaction and for centred speech rate.[^1] The categorical predictors vowel and C2 are coded using indexing rather than traditional R contrasts: in R, this corresponds to suppressing the model's intercept with the `0 +` syntax; using indexing instead of contrasts makes it easier to specify priors. For pedagogical simplicity, the model will use the default priors, but note that in real data analyses contexts, priors should be specified by the user. I refer the readers to XXX.

[^1]: Footnote about Gelman's terminology for random effects.

@@

The `summary()` function prints the full model summary. For conciseness, we will use the `fixef()` function which prints the regression coefficients. \[EXPLAIN EXPECTED PREDICTIONS XXX\]. The full summary with an explanation of each part can be found in XXX. @tbl-voi-prop-fixef reports the output of `fixef()` as a table (we round all values to the nearest 2 digits for clarity.). For each coefficient in the model, `fixef()` prints the name of the coefficient, the mean estimate, the estimate error and the lower and upper limits of a Bayesian Credible interval (CrI). Here, we print an 80% CrI. There is nothing special about 95% CrI within Bayesian inference and instead experts recommend to check and report a variety of CrIs. Obtaining CrIs at different probability levels allows researchers to make more fine-grained inferential statements than the frequentist significance dichotomy affords. For simplicity of exposition, we will use 80% CrIs in this case study but we strongly recommend researchers to always obtain CrIs at different levels of probability and base their inferences on all and not one in particular. To reiterate, in Bayesian inference, an 80% CrI indicates the range of values within which the true estimate falls at 80% probability or confidence.

@@

The coefficients of a beta regression are estimated on the log-odds scale, as in Bernoulli/binomial (aka logistic) regressions. From the summary, we see that speech rate (number of syllables per second) has a positive effect on voicing proportion: the 80% CrI is between 0.01 and 0.15 log-odds \[$\beta$ = 0.08, SD = 0.06\]. Log-odds can be converted to odd-ratios by exponentiating the value: 0.01-0.15 log odds correspond to an odd-ratio of 1.01 to 1.16, or as percentages, to an increase of voicing of 1 to 16% for every increase of one syllable per second. Since this is an 80% CrI, we can be 80% confident that the true effect of speech rate is between 1-16% increase of voicing proportion, conditional on the data and model. Note that transforming measures this way is appropriate *only* with quantile-based measures (like CrIs) but not with moments like the mean and standard deviation: to correctly get mean and SDs in the transformed scale, you must first extract the posterior draws (see below), convert them and then take moments such as mean and SD (for a more detailed explanation, see XXX). In the avoidance of doubt, we will always transform the drawn values first and then take summary measures.

>>>>

The main practical advantage of Bayesian regression models over maximum-likelihood-based frequentist regression models, like those fitted with the lme4 package [@bates2015], is that Bayesian regression models don't suffer from the convergence issues that models fitted in lme4 [@bates2015] and other packages [@cribarineto2010] that fit frequentist models do, independent of sample size. A second, long-term advantage is that Bayesian regression models allow researchers to statistically re-use information from previous studies by specifying informative priors. While prior specification is one of the main features of Bayesian inference, in this tutorial we will use the default priors as set by brms. These are sensible priors estimated from the data that facilitate convergence but bear virtually no influence on the estimated posteriors. Specifying priors requires a great deal of precise quantitative knowledge, which in most areas of phonetics we still do not possess, so that using default uninformative priors is, for the time being, theoretically sound. For practical guidance on prior specification, see <https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations>.

@@

# Case study 1: coarticulatory voicing within consonant closure {#sec-case-1}

For the first case study, we will model the proportion of coarticulatory progressive voicing within the consonant closure of voiceless stops. The measurements come from a data set of audio and electroglottographic (EGG) recordings of 19 speakers of Northwestern Italian [@coretta2019k; @coretta2020b]. The participants read frame sentences which included target words of the form /CVCo/, where C was either /k, t, p/ in all permutations and V was either /i, e, a, o, u/ (two resulting words, /peto/ and /kako/ were excluded because they are profanities), for a total of 43 target words. There were 4 different frame sentence: *Scrivete X sul foglio* 'Write X on the sheet', *Ha detto X sei volte* 'She said X six times', *Sentivo X di nuovo* 'I heard X again', *Ripete X da sempre* 'She's been repeating X since ever'. There is a total of 172 trials per participant (3,268 grand total). The actual observation count is 2,419, after removing speech errors, EGG measurement errors, and cases in which voicing ceased before the closure onset/after the closure offset of the second consonant in the target word.

The proportion of voicing during the closure of the second consonant was calculated as the proportion of contiguous voicing duration after closure onset to total duration of closure. The following code chunk attaches the tidyverse packages [for reading and wrangling data, @wickham2019] and loads the `ita_egg` tibble (data frame). The tibble is filtered so as to remove voicing proportions (`voi_clo_prop`) that are smaller than 0 and greater than 1. The variables `vowel` (first vowel in the target word) and `c2` (second consonant in the target word) are converted to factors to specify the order of the levels. @tbl-ita-egg shows the first ten rows of the tibble (only relevant columns are included).

@@

@@

@fig-ita-egg shows the raw voicing duration proportion values split by vowel /i, e, a, o, u/ and second consonant /k, t, p/ in the /CVCo/ target words. The plot suggests that, on average, the voicing proportion is slightly lower with /k/ than with /t, p/. Moreover, there is greater variability between vowels in /t, p/ than in /k/. We will use a beta regression model to assess whether the place of articulation of the consonant affects the proportion of coarticulatory progressive voicing, while averaging across vowels (of course, another question that could be answered with the same model is if different vowels lead to difference voicing proportions, but for sake of space we restrict this tutorial to the former question). A general expectation is that the proportion of progressive voicing should increase with fronter places of articulation (so from /k/ to /t/ to /p/) given the aerodynamic constraints which obtain with vocal fold vibration during a fully occluded oral tract [@vandenberg1958; @rothenberg1967; @ohala2011].

@@

We will use brms to fit a Bayesian beta regression [@burkner2017]. The model has voicing proportion as the outcome variable and the following terms: an interaction between vowel (/i, e, a, o, u/) and second consonant C2 (/k, t, p/), centred speech rate (number of syllables per second); as varying (aka random) terms, we included by-speaker varying coefficients for the vowel/consonant interaction and for centred speech rate.[^1] The categorical predictors vowel and C2 are coded using indexing rather than the traditional R contrasts: in R, this corresponds to suppressing the model's intercept with the `0 +` syntax; using indexing instead of contrasts makes it easier to specify priors and uncertainty is distributed equally across all levels of categorical predictors. For pedagogical simplicity, the model will use the default priors as explained in @sec-bayes.

[^1]: While the terms "random effects, intercept and slopes" are commonly employed in applied statistical work in linguistics and phonetics, we opt to use the conceptually more appropriate terminology proposed by @gelman2005: varying terms, intercepts, slopes, coefficients. Other common terms are multilevel and hierarchical terms.

@@

The `summary()` function prints the full model summary. For conciseness, we will use the `fixef()` function which prints the regression coefficients. The full summary with an explanation of each part can be found in XXX. @tbl-voi-prop-fixef reports the output of `fixef()` as a table (we round all values to the nearest 2 digits for clarity.). For each coefficient in the model, `fixef()` prints the name of the coefficient, the mean estimate, the estimate error and the lower and upper limits of a Bayesian Credible interval (CrI). Note that all values are in log-odds, since the link function in beta regressions is the logistic function, like in binomial/Bernoulli regressions. Here, we print an 80% CrI. There is nothing special about 95% CrI within Bayesian inference and instead experts recommend to check and report a variety of CrIs. Obtaining CrIs at different probability levels allows researchers to make more fine-grained inferential statements than the frequentist significance dichotomy affords. For simplicity of exposition, we will use 80% CrIs in this case study but we strongly recommend researchers to always obtain CrIs at different levels of probability and base their inferences on all and not one in particular. To reiterate, in Bayesian inference, an 80% CrI indicates the range of values within which the true estimate falls at 80% probability or confidence.

@@

From the summary, we see that speech rate (number of syllables per second) has a positive effect on voicing proportion: the 80% CrI is between 0.01 and 0.15 log-odds [$\beta$ = 0.08, SD = 0.06]. Log-odds can be converted to odd-ratios by exponentiating the value: 0.01-0.15 log odds correspond to an odd-ratio of 1.01 to 1.16, or as percentages, to an increase of voicing of 1 to 16% for every increase of one syllable per second. Since this is an 80% CrI, we can be 80% confident that the true effect of speech rate is between 1-16% increase of voicing proportion, conditional on the data and model. Note that transforming measures this way is appropriate *only* with quantile-based measures (like CrIs) but not with moments like the mean and standard deviation: to correctly get mean and SDs in the transformed scale, you must first extract the posterior draws (see below), convert them and then take moments such as mean and SD [for a more detailed explanation, see @burkner2025, p. 101]. In the avoidance of doubt, we will always transform the drawn values first and then take summary measures.

### 2025-02-06 manuscript/manuscript.tex
edit manuscript

The main practical advantage of Bayesian regression models over
maximum-likelihood-based frequentist regression models, like those
fitted with the lme4 package \citep{bates2015}, is that Bayesian
regression models don't suffer from the convergence issues that models
fitted in lme4 \citep{bates2015} and other packages
\citep{cribarineto2010} that fit frequentist models do, independent of
sample size. A second, long-term advantage is that Bayesian regression
models allow researchers to statistically re-use information from
previous studies by specifying informative priors. While prior
specification is one of the main features of Bayesian inference, in this
tutorial we will use the default priors as set by brms. These are
sensible priors estimated from the data that facilitate convergence but
bear virtually no influence on the estimated posteriors. Specifying
priors requires a great deal of precise quantitative knowledge, which in
most areas of phonetics we still do not possess, so that using default
uninformative priors is, for the time being, theoretically sound.

@@

\section{Case study 1: voicing within consonant
closure}\label{sec-case-1}

For the first case study, we will model the proportion of voicing within
consonant closure. The measurements come from a data set of audio and
electroglottographic (EGG) recordings of 19 speakers of Northwestern
Italian \citep{coretta2019k, coretta2020b}. The participants read frame
sentences which included target words of the form /CVCo/, where /C/ was
either /k, t, p/ in all permutations and /V/ was either /i, e, a, ɔ, u/
(two resulting words, /peto/ and /kako/ were excluded because they are
profanities), for a total of 43 target words. There were 4 different
frame sentence: \emph{Scrivete X sul foglio} `Write X on the sheet',
\emph{Ha detto X sei volte} `She said X six times', \emph{Sentivo X di
nuovo} `I heard X again', \emph{Ripete X da sempre} `She's been
repeating X since ever'. There is a total of 172 trials per participant
(3,268 grand total). The actual observation count is 2,419, after
removing speech errors, EGG measurement errors, and cases in which
voicing ceased before the closure onset/after the closure offset of the
second /C/.

The proportion of voicing during the closure of the second /C/ was
calculated as the proportion of contiguous voicing duration after
closure onset to total duration of closure. The following code chunk
attaches the tidyverse packages \citep[for reading and wrangling
data,][]{wickham2019} and loads the \texttt{ita\_egg} tibble (data
frame). The tibble is filtered so as to remove voicing proportions
(\texttt{voi\_clo\_prop}) that are smaller than 0 and greater than 1.
The variables \texttt{vowel} and \texttt{c2} are converted to factors to
specify the order of the levels.

@@

Table~\ref{tbl-ita-egg} shows the first ten rows of the tibble (only
relevant columns are included).

@@

Figure~\ref{fig-ita-egg} shows the raw voicing duration proportion
values split by vowel /i, e, a, ɔ, u/ and second consonant /k, t, p/ in
the /CVCo/ target words. The plot suggests that, on average, the voicing
proportion is slightly lower with /k/ than with /t, p/. Moreover, there
is greater variability between vowels in /t, p/ than in /k/. We will use
a beta regression model to assess these patterns. {[}``expectations''
XXX{]}

@@

We will use brms to fit Bayesian beta regressions \citep{burkner2017}.
The model has voicing proportion as the outcome variable and the
following terms: an interaction between vowel (/i, e, a, ɔ, u/) and
second consonant C2 (/k, t, p/), centred speech rate (number of
syllables per second); as varying (aka random) terms, by-speaker varying
coefficients for the vowel/consonant interaction and for centred speech
rate.\footnote{Footnote about Gelman's terminology for random effects.}
The categorical predictors vowel and C2 are coded using indexing rather
than traditional R contrasts: in R, this corresponds to suppressing the
model's intercept with the \texttt{0\ +} syntax; using indexing instead
of contrasts makes it easier to specify priors. For pedagogical
simplicity, the model will use the default priors, but note that in real
data analyses contexts, priors should be specified by the user. I refer
the readers to XXX.

@@

The \texttt{summary()} function prints the full model summary. For
conciseness, we will use the \texttt{fixef()} function which prints the
regression coefficients. {[}EXPLAIN EXPECTED PREDICTIONS XXX{]}. The
full summary with an explanation of each part can be found in XXX.
Table~\ref{tbl-voi-prop-fixef} reports the output of \texttt{fixef()} as
a table (we round all values to the nearest 2 digits for clarity.). For
each coefficient in the model, \texttt{fixef()} prints the name of the
coefficient, the mean estimate, the estimate error and the lower and
upper limits of a Bayesian Credible interval (CrI). Here, we print an
80\% CrI. There is nothing special about 95\% CrI within Bayesian
inference and instead experts recommend to check and report a variety of
CrIs. Obtaining CrIs at different probability levels allows researchers
to make more fine-grained inferential statements than the frequentist
significance dichotomy affords. For simplicity of exposition, we will
use 80\% CrIs in this case study but we strongly recommend researchers
to always obtain CrIs at different levels of probability and base their
inferences on all and not one in particular. To reiterate, in Bayesian
inference, an 80\% CrI indicates the range of values within which the
true estimate falls at 80\% probability or confidence.

@@

The coefficients of a beta regression are estimated on the log-odds
scale, as in Bernoulli/binomial (aka logistic) regressions. From the
summary, we see that speech rate (number of syllables per second) has a
positive effect on voicing proportion: the 80\% CrI is between 0.01 and
0.15 log-odds {[}\(\beta\) = 0.08, SD = 0.06{]}. Log-odds can be
converted to odd-ratios by exponentiating the value: 0.01-0.15 log odds
correspond to an odd-ratio of 1.01 to 1.16, or as percentages, to an
increase of voicing of 1 to 16\% for every increase of one syllable per
second. Since this is an 80\% CrI, we can be 80\% confident that the
true effect of speech rate is between 1-16\% increase of voicing
proportion, conditional on the data and model. Note that transforming
measures this way is appropriate \emph{only} with quantile-based
measures (like CrIs) but not with moments like the mean and standard
deviation: to correctly get mean and SDs in the transformed scale, you
must first extract the posterior draws (see below), convert them and
then take moments such as mean and SD (for a more detailed explanation,
see XXX). In the avoidance of doubt, we will always transform the drawn
values first and then take summary measures.

>>>>

The main practical advantage of Bayesian regression models over
maximum-likelihood-based frequentist regression models, like those
fitted with the lme4 package \citep{bates2015}, is that Bayesian
regression models don't suffer from the convergence issues that models
fitted in lme4 \citep{bates2015} and other packages
\citep{cribarineto2010} that fit frequentist models do, independent of
sample size. A second, long-term advantage is that Bayesian regression
models allow researchers to statistically re-use information from
previous studies by specifying informative priors. While prior
specification is one of the main features of Bayesian inference, in this
tutorial we will use the default priors as set by brms. These are
sensible priors estimated from the data that facilitate convergence but
bear virtually no influence on the estimated posteriors. Specifying
priors requires a great deal of precise quantitative knowledge, which in
most areas of phonetics we still do not possess, so that using default
uninformative priors is, for the time being, theoretically sound. For
practical guidance on prior specification, see
\url{https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations}.

@@

\section{Case study 1: coarticulatory voicing within consonant
closure}\label{sec-case-1}

For the first case study, we will model the proportion of coarticulatory
progressive voicing within the consonant closure of voiceless stops. The
measurements come from a data set of audio and electroglottographic
(EGG) recordings of 19 speakers of Northwestern Italian
\citep{coretta2019k, coretta2020b}. The participants read frame
sentences which included target words of the form /CVCo/, where C was
either /k, t, p/ in all permutations and V was either /i, e, a, o, u/
(two resulting words, /peto/ and /kako/ were excluded because they are
profanities), for a total of 43 target words. There were 4 different
frame sentence: \emph{Scrivete X sul foglio} `Write X on the sheet',
\emph{Ha detto X sei volte} `She said X six times', \emph{Sentivo X di
nuovo} `I heard X again', \emph{Ripete X da sempre} `She's been
repeating X since ever'. There is a total of 172 trials per participant
(3,268 grand total). The actual observation count is 2,419, after
removing speech errors, EGG measurement errors, and cases in which
voicing ceased before the closure onset/after the closure offset of the
second consonant in the target word.

The proportion of voicing during the closure of the second consonant was
calculated as the proportion of contiguous voicing duration after
closure onset to total duration of closure. The following code chunk
attaches the tidyverse packages \citep[for reading and wrangling
data,][]{wickham2019} and loads the \texttt{ita\_egg} tibble (data
frame). The tibble is filtered so as to remove voicing proportions
(\texttt{voi\_clo\_prop}) that are smaller than 0 and greater than 1.
The variables \texttt{vowel} (first vowel in the target word) and
\texttt{c2} (second consonant in the target word) are converted to
factors to specify the order of the levels. Table~\ref{tbl-ita-egg}
shows the first ten rows of the tibble (only relevant columns are
included).

@@

@@

Figure~\ref{fig-ita-egg} shows the raw voicing duration proportion
values split by vowel /i, e, a, o, u/ and second consonant /k, t, p/ in
the /CVCo/ target words. The plot suggests that, on average, the voicing
proportion is slightly lower with /k/ than with /t, p/. Moreover, there
is greater variability between vowels in /t, p/ than in /k/. We will use
a beta regression model to assess whether the place of articulation of
the consonant affects the proportion of coarticulatory progressive
voicing, while averaging across vowels (of course, another question that
could be answered with the same model is if different vowels lead to
difference voicing proportions, but for sake of space we restrict this
tutorial to the former question). A general expectation is that the
proportion of progressive voicing should increase with fronter places of
articulation (so from /k/ to /t/ to /p/) given the aerodynamic
constraints which obtain with vocal fold vibration during a fully
occluded oral tract \citep{vandenberg1958, rothenberg1967, ohala2011}.

@@

We will use brms to fit a Bayesian beta regression \citep{burkner2017}.
The model has voicing proportion as the outcome variable and the
following terms: an interaction between vowel (/i, e, a, o, u/) and
second consonant C2 (/k, t, p/), centred speech rate (number of
syllables per second); as varying (aka random) terms, we included
by-speaker varying coefficients for the vowel/consonant interaction and
for centred speech rate.\footnote{While the terms ``random effects,
  intercept and slopes'' are commonly employed in applied statistical
  work in linguistics and phonetics, we opt to use the conceptually more
  appropriate terminology proposed by \citet{gelman2005}: varying terms,
  intercepts, slopes, coefficients. Other common terms are multilevel
  and hierarchical terms.} The categorical predictors vowel and C2 are
coded using indexing rather than the traditional R contrasts: in R, this
corresponds to suppressing the model's intercept with the \texttt{0\ +}
syntax; using indexing instead of contrasts makes it easier to specify
priors and uncertainty is distributed equally across all levels of
categorical predictors. For pedagogical simplicity, the model will use
the default priors as explained in Section~\ref{sec-bayes}.

@@

The \texttt{summary()} function prints the full model summary. For
conciseness, we will use the \texttt{fixef()} function which prints the
regression coefficients. The full summary with an explanation of each
part can be found in XXX. Table~\ref{tbl-voi-prop-fixef} reports the
output of \texttt{fixef()} as a table (we round all values to the
nearest 2 digits for clarity.). For each coefficient in the model,
\texttt{fixef()} prints the name of the coefficient, the mean estimate,
the estimate error and the lower and upper limits of a Bayesian Credible
interval (CrI). Note that all values are in log-odds, since the link
function in beta regressions is the logistic function, like in
binomial/Bernoulli regressions. Here, we print an 80\% CrI. There is
nothing special about 95\% CrI within Bayesian inference and instead
experts recommend to check and report a variety of CrIs. Obtaining CrIs
at different probability levels allows researchers to make more
fine-grained inferential statements than the frequentist significance
dichotomy affords. For simplicity of exposition, we will use 80\% CrIs
in this case study but we strongly recommend researchers to always
obtain CrIs at different levels of probability and base their inferences
on all and not one in particular. To reiterate, in Bayesian inference,
an 80\% CrI indicates the range of values within which the true estimate
falls at 80\% probability or confidence.

@@

From the summary, we see that speech rate (number of syllables per
second) has a positive effect on voicing proportion: the 80\% CrI is
between 0.01 and 0.15 log-odds {[}\(\beta\) = 0.08, SD = 0.06{]}.
Log-odds can be converted to odd-ratios by exponentiating the value:
0.01-0.15 log odds correspond to an odd-ratio of 1.01 to 1.16, or as
percentages, to an increase of voicing of 1 to 16\% for every increase
of one syllable per second. Since this is an 80\% CrI, we can be 80\%
confident that the true effect of speech rate is between 1-16\% increase
of voicing proportion, conditional on the data and model. Note that
transforming measures this way is appropriate \emph{only} with
quantile-based measures (like CrIs) but not with moments like the mean
and standard deviation: to correctly get mean and SDs in the transformed
scale, you must first extract the posterior draws (see below), convert
them and then take moments such as mean and SD \citep[for a more
detailed explanation, see][p.~101]{burkner2025}. In the avoidance of
doubt, we will always transform the drawn values first and then take
summary measures.
